Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-22 SupportingInformation.Rmd
for rlist and Klist100,1000 for all uniparameter family

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```

@@

model<-"ricker"
fcode<-13

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-4

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-14

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-6

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-16

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(i in rlist){
  params<-c(i,100) # this parameter is a vector with r and K
  p0<-c(params[2],params[2])

@@

# for survival joe with kendall method only

  Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

>>>>

Klist<-c(100,1000)

# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)
#rlist<-c(0.5,1.1)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
}
```

@@

model<-"ricker"
fcode<-13
Klist<-c(100,1000)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-4
Klist<-c(100,1000)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-14
Klist<-c(100,1000)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-6
Klist<-c(100,1000)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

model<-"ricker"
fcode<-16
Klist<-c(100,1000)
# for varying r (@r=1 transition from under- to over-compensatory dynamics )
rlist<-seq(from=0.1,to=1.3,by=0.2)

for(iK in Klist){
  for(i in rlist){
    params<-c(i,iK) # this parameter is a vector with r and K
    p0<-c(params[2],params[2])

@@

    Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=fcode,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=p0,model=model)
  }
}
```
<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}
